---
title: "modelBuildR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{modelBuildR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(modelBuildR)
```

## Load data 
```{r}
meta <- read.csv(paste(system.file("extdata", package="modelBuildR"), "/meta.csv",sep=""), row.names=1)
data <- read.csv(paste(system.file("extdata", package="modelBuildR"), "/data_m.csv", sep=""), row.names=1)

ggplot2::ggplot(meta, ggplot2::aes(x=CONT)) + ggplot2::geom_histogram()
ggplot2::ggplot(meta, ggplot2::aes(x=BIN)) + ggplot2::geom_histogram()
```

# Logistic regression: binary classification

## Create instance 
```{r}
# Please assure manually that order of cols of data corresponds
# to order of rows in meta

obj <- new("fitModel", data, meta, var="BIN", type="lr")
```

## test differences 
Test influence of grouping covariate (will be the predicted variable)
on the dependent variables (features)

Likelihood ratio test p-value (per model) to select features.

```{r}
## no covar
obj <- testSign(obj, pCut=0.05, pAdj="none")

### with covariates
objC <- testSign(obj, pCut=0.05, pAdj="none", 
		frm0=as.formula(VAL~CONT),
		frm=as.formula(VAL~CONT+BIN))
```

## crossvalidation  
```{r}
obj <- cv(obj)

## w/ covar
objC <- cv(objC, frm="~CONT+BIN")
```

## model fitting 
```{r warning=FALSE}
obj <- fitM(obj)
fit <- obj@model
fit

###covar
objC <- fitM(objC)
objC@model
```

## plot
```{r}
### obtain model predictions
pr <- predict(fit, newdata=data.frame(t(obj@dataSign)), interval="prediction", se.fit=T)
df <- data.frame(do.call(cbind, pr), obj@meta)
df <- df[order(df[,1]),]
df$x <- 1:length(df[,1])
ggplot2::ggplot(df, ggplot2::aes(y=fit, x=x, col=factor(BIN))) + ggplot2::geom_point() #+ ggplot2::geom_errorbar(ggplot2::aes(ymin=fit-se.fit, ymax=fit+se.fit)) 
rocDetail(df$fit, df$BIN)

### 
pr <- predict(fit, type="response", newdata=data.frame(t(obj@dataSign)), interval="prediction", se.fit=T)
df <- data.frame(do.call(cbind, pr), obj@meta)
df <- df[order(df[,1]),]
df$x <- 1:length(df[,1])
ggplot2::ggplot(df, ggplot2::aes(y=fit, x=x, col=factor(BIN))) + ggplot2::geom_point() + ggplot2::geom_errorbar(ggplot2::aes(ymin=fit-se.fit, ymax=fit+se.fit)) 
rocDetail(df$fit, df$BIN)
```


# Linear regression

## Create instance 
```{r}
# Please assure manually that order of cols of data corresponds
# to order of rows in meta
obj <- new("fitModel", data, meta, var="CONT", type="lm")
```

## test differences 
Test influence of grouping covariate (will be the predicted variable)
on the dependent variables (features)

Likelihood ratio test p-value (per model) to select features.

```{r}
obj <- testSign(obj, pCut=0.05, pAdj="none")

### with covariates
objC <- testSign(obj, pCut=0.05, pAdj="none", 
		frm0=as.formula(VAL~CONT),
		frm=as.formula(VAL~CONT+BIN))

```

## crossvalidation 
```{r}
## non adjusted
obj <- cv(obj)

##adjusted
objC <- cv(obj, frm="~CONT+BIN")
```

## model fitting 
```{r warning=FALSE}
obj <- fitM(obj)
fit <- obj@model
fit

###covar
objC <- fitM(objC)
objC@model
```

## plot
```{r}
### obtain model predictions
pr <- predict(fit, newdata=data.frame(t(obj@dataSign)), interval="prediction", se.fit=T)
df <- data.frame(do.call(cbind, pr), obj@meta)
df <- df[order(df[,1]),]
df$x <- 1:length(df[,1])
ggplot2::ggplot(df, ggplot2::aes(y=fit, x=x, col=factor(CONT))) + ggplot2::geom_point() + ggplot2::geom_errorbar(ggplot2::aes(ymin=fit-se.fit, ymax=fit+se.fit))
```

